---
title: "Gov 50 Final Project"
author: "Luca Ace-Nasteski"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

I am interested in exploring data related to basketball, salaries, rankings and statistics. In particular how the top 100 "ranked" players in high-school's salaries turned out, or the longevity of their career in both college and/or the NBA. How many of these players actually make the NBA? How many stay for more than five years? What about the data for those who aren't in the rankings and make the NBA? International? etc.

1. Do certain defensive statistics impact NBA player's minutes and effectiveness towards winning?
2. Defensive statistics to a degree will likely impact a player's minutes and contribute to their impact on their respective teams.
3. The explanatory variable are changes in defensive statistics (great/worse) for steals, blocks, rebounds, deflections, etc.
4. The outcome variable is how many minutes the NBA player plays as a result and how many wins their team gets during the season. It will be measured by minutes played, plus-minus effect on the game and team win share.
5. That defense is the fundamental of the game and in the data set greater defensive statistics already mean you are playing and making a great impact. I would like to see though the players that do not play as much yet still have great defensive statistics and see how much they actually impact the game. This may be disproved in the statistics because little playing time often correlates to lower percentages and opportunity for defensive statistics.

## Loading in... 

```{r}
library(tidyverse)
library(ggplot2)
nba <- read_csv("nba-data-historical.csv")
```

# Visualisation of data

```{r}
nba <- nba |>
  group_by(team_id, age) |>
  summarize(count = n()) |>
  mutate(proportion = count/sum(count))

nba |>
  ggplot(mapping = aes(x = team_id, y = proportion, fill = age)) + 
  geom_col(position = "dodge") 

```



